---
title: 'dapr1: Lab test'
author: '[B153904]'
date: "25/11/2019"
output: html_document

---

PLEASE RUN THE CODE CHUNK UNDERNEATH THIS TEXT BEFORE YOU START THE QUESTIONS. BEFORE YOU RUN THE CHUNK, PLEASE ASSIGN YOUR EXAM NUMBER (EXCLUDING LETTERS) TO THE OBJECT `X`. SO FOR EXAMPLE, IF YOUR EXAM NUMBER IS B100001, YOU LINE 11 WILL READ `X <- 100001`

```{r, echo=FALSE, warning=FALSE, message=FALSE}

## Packages
library(tidyverse)

## Add the numbers from your exam number here
x <- 153904

##DO NOT CHANGE ANY OF THE FOLLOWING CODE
set.seed(x)
n <- sample(100:200, 1)
ID <- paste("ID", 1:n, sep="")

set.seed(x)
Age <- round(rnorm(n=n, mean = sample(seq(30,35,0.2)), sd = sample(seq(1,3,0.25))),0)

set.seed(x)
Score <- round(rnorm(n=n, mean = sample(seq(30,50,1)), sd = sample(seq(6,10,1))),0)

set.seed(x)
Group <- factor(sample(c("Group1","Group2","Group3" ), n, replace = TRUE, prob = c(0.4,0.4,0.2)))

set.seed(x)
Smoke <- factor(sample(c("No","Yes"), n, replace = TRUE, prob = c(0.8,0.2)))

df <- tibble(ID, Age, Score, Group, Smoke) 
head(df)
```

## DATA
You should now have a data set in your R environment called `df`. The first six rows of which should be printed immediately above. 

This data set has five variables labelled ID, Age, Score, Group and Smoke. The variables are described below: 

- ID = ID variable for each participant.
- Age = Age of participants. Numeric variable. 
- Score = A self-rated health score (range 1-100). Numeric variable.
- Group = Study condition. Factor with 3 levels; "Group1", "Group2", "Group3".
- Smoke = Do you smoke? Factor with two levels; "No", "Yes".

For questions 1 to 4 below, save your answer as an object, and then print the object within the code chunk (the last line of the chunk should contain only the object name). This is important for attempting question 5.

## QUESTION 1
Calculate the median of `Age` and `Score` for the participants who do not smoke. 

```{r}
Median_Age <- df %>%
  filter(Smoke == "No") %>%
  summarise(median_Age = median(Age))
Median_Age
Median_Score <- df %>%
  filter(Smoke == "No") %>%
  summarise(median_Score = median(Score))
Median_Score
```

## QUESTION 2
Show how many smokers there are in Group 1.

```{r}
smokers_in_Group1 <- df %>%
  filter(Smoke == "Yes") %>%
  filter(Group == "Group1") %>%
  count(Smoke)
smokers_in_Group1
```

## QUESTION 3
Produce a plot to show the distribution of `Score` by each level of `Group`.

```{r}
ggplot(data = df, aes(x = Group, y = Score, fill = Group)) +
  geom_boxplot() + theme_minimal() +
  scale_fill_brewer(palette = "Purples")
  labs(x = "Groups", y = "Scores of Each Level", title = "Distribution of Score by Groups")
```


## QUESTION 4
Create a new tibble containing only students with `Score` lower than 25?

```{r}
Scorelowerthan25 <- df %>%
  filter(Score < 25)
Scorelowerthan25
Students <- tibble(Students = Scorelowerthan25$ID)
Students
```


## QUESTION 5: Difficult question - in line code
Write a short summary (one or two sentences) summarising one of the questions above using in line R-code to insert the results from your analyses.

Add your sentence below:
Q1: Throughout the data given above, the median age of participants who do not smoke is `r Median_Age`, and the median self-rated health score of participants who do not smoke is `r Median_Score`.

